\section{Introduction}

\subsection{Overview of Domain}

% Personal informatics

Personal informatics is a term used to refer to devices and software that help people gather
information about themselves, so they can reflect upon it and gain motivation to make changes to
their lifestyle and habits to improve their overall wellbeing. Personal informatics is used for
effectively motivating people to gain self-knowledge, change behaviours. % Gen's source here

The area of personal informatics has started to expand in popularity in recent years mainly due to
the increased availability and usability of affordable hardware. Consumer products such as the
FitBit and Apple Watch allow users to collect data on a wide variety of metrics including heart
rate, blood pressure, motion and many others. Products such as the Neuroon, a wearable EEG eye mask,
and Zeo Sleep Manager Pro, an EEG headband, allow the user to collect information on brain waves for
the purpose of sleep tracking.
% Validity of Consumer Activity Wristbands and Wearable EEG for Measuring Overall Sleep Parameters
% and Sleep Structure in Free-Living Conditions,

% Consumer Sleep Tracking Devices: A Critical Review in Digital Healthcare Empowering Europeans -
% write more here about other devices

Another factor that has contributed to the growth of personal informatics is the ubiquity of
smartphones, meaning that users have an ever-present device that allows them to collect and collate
data from their personal informatics hardware. Many personal informatics apps also add an element of
socially driven competition and gamification, driving users' motivation to continue to use them and
push their friends to also begin using this technology. In addition, there is a larger social force
pushing people to take steps to improve themselves. % Expand on this sentence

% Gamification!!

\subsection{Challenges}
Although personal informatics systems for wellbeing has been on the rise, it inherently presents flaws that need to
be taken into account. In a survey conducted by / where participants were regular personal informatics users it was revealed
that the most significant shortcomings of personal informatics systems supplied by commercial companies was a lack of understanding
for the end user's requirements and an absence of assistance and alerts for users who didn't meet their goals.
Apart from users who are familiar with personal informatics systems it is also important to consider the challenges
faced by the common user; a user who is new to using a personal informatics device. It was discovered by / that the main
challenge for personal informatics systems was the lack of motivation faced by the end user to continue to use the system.
These challenges need to be taken into account because these hinder the end user from improving themselves which is contradictory
to the goal of personal informatics systems.

\subsubsection{Privacy and Security of Data}

% Data has to be stored somewhere, it's often being collected through third-party apps, no way to
% ensure it isn't transmitted or stored elsewhere

% Scraping of data with Cambridge Analytica, Strava military base heatmap

\subsubsection{Health Risks}

One crucial problem in the realm of health is sleep deprivation. Sleep deprivation is defined by
\textcite{BMA:2018aa} as ``a lack of sufficient sleep resulting from disruption to the natural sleep
cycle''. This is important to highlight because as as opposed to fatigue, sleep deprivation isn't
subjective. In accordance to \textcite{Alhola:2007aa}, it was estimated that the main effect of
sleep deprivation was the reduction in cognitive performance. This includes: impaired attention;
longer delays in making decisions; poor quality of decisions and a reduction in long memory. This is
especially important to monitor for individuals who have high risk jobs. In 2010, passenger's lives
were lost when a plane overshot the runway by 600 meters; although concrete details haven't been
exposed, it was claimed that the accident unfolded due to the pilot's severe sleep deprivation
\parencite{BBC:2010aa}. Even in circumstances where the individual isn't responsible for people's
lives, a reduction in cognitive performance is still observed. Hence, the validity of this problem
is justified.

Sleep deprivation has the potential to be a dangerous to anyone and
even fatal, if it is not identified and managed.Over a third of adults get less than seven hours
of sleep during a typical 24-hour period.Lack of sleep affects a person's abilities and health
in many ways and can limit their ability to perform in their line of work.This can be seriously,
especially for professions that the general public’s lives rely on greatly such as doctors and nurses.
Each year, 100,000 deaths occur in US hospitals due to medical errors and sleep deprivation in the
medical staff has been shown to contribute to this statistic.(Sleep Association) Driving whilst feeling drowsy
has been shown to be similar to driving whilst under the influence of alcohol and can be attributed to a
portion of car collisions each year. (Sleep Foundation) There are few visible indications that an individual
is getting less sleep than recommended and it’s difficult to know if you are deprived of sleep
which often makes it more damaging as it may be challenging to identify and then attempt to curb.
Similarly, there’s no legal limit for sleep deprivation for situations such as driving a vehicle.
Sleep deprivation is to measure without the external equipment.

\subsubsection{Solution}

Our software system aims to reduce fatigue in individuals due to a lack of sleep.
 EEG have the ability to detect sleeping problems based on brain wave patterns. (Mayfield Clinic)
 Monitoring and recording the individual user’s brainwave data during their sleep allows the system
 to be tailored specifically for that individual. Implementation of a points system would ensure the
 user regularly uses the headset. If the system were to be used most nights, the headset would be able
 to measure and record a large quantity of reliable data for the system to process making results
 recommendations the system provides likely to be accurate and therefore helpful to the user.
 If the data were to be displayed in a format easily, this would help the user
 to better understand their recorded sleep data and allow them to make more appropriate decisions as to
 how to change their actions.
