% Definitions of the requirements

\setreqsec{soft-devel}{Software Development Process}

\setreq{agile-scrum}
{The system must adhere to the Agile/Scrum methodology.}
{\phigh}
{\dnone}
{\sspec}

\setreq{3-sprints}
{Software development should include at least 3 sprints.}
{\pmed}
{\ref{req:agile-scrum}, \ref{req:1-3-weeks}}
{\sspec}

\setreq{1-3-weeks}
{Each sprint should last between 1 and 3 weeks.}
{\pmed}
{\ref{req:agile-scrum}, \ref{req:3-sprints}}
{\sspec}

\setreq{review-reqs}
{Must review the functional requirements at every scrum meeting.}
{\phigh}
{\ref{req:1-3-weeks}}
{\sspec}

\setreq{risk-management}
{Must incorporate risk management into the software process.}
{\phigh}
{\ref{req:agile-scrum}}
{\sspec}

\setreqsec{expanding-initial}{Expanding Initial Requirements}

\setreq{expand-non-func}
{The system must expand upon the initial non-functional requirements.}
{\phigh}
{\dnone}
{\sspec}

\setreq{expand-func}
{The system must expand upon the initial functional requirements and add additional functionality
  to the system.}
{\phigh}
{\dnone}
{\sspec}

\setreq{additional-reqs}
{Additional requirements should be established by conducting interviews on potential users,
  reading articles on personal informatics and examining existing personal informatics systems.}
{\phigh}
{\ref{req:expand-non-func}, \ref{req:expand-func}}
{\sspec}

\setreqsec{background-research}{Background Research}

\setreq{4-articles}
{Must read and cite 4 articles in the field of personal informatics.}
{\phigh}
{\dnone}
{\sspec}

\setreq{8-articles}
{Should read and cite at least eight articles.}
{\pmed}
{\dnone}
{\sspec}

\setreq{core-peer-reviewed}
{Citations of core article must be peer-reviewed articles.}
{\phigh}
{\ref{req:4-articles}}
{\sspec}

\setreq{additional-web}
{Additional citations may be made to web articles of unknown quality.}
{\plow}
{\dnone}
{\sspec}

\setreq{classify-rem-cycles}
{Must classify measurements of stages of sleep (REM cycles).}
{\phigh}
{\dnone}
{\textcite{Tuck:2018aa}, \textcite{Feinberg:1988aa}, \textcite[p.291]{Carlson:2012aa}}

\setreqsec{ethical-issues}{Ethical Issues}

\setreq{ethical-issues}
{Must account for ethical issues in the specification, design, development and testing of the
  system.}
{\phigh}
{\dnone}
{\sspec}

\setreqsec{testing}{Testing}

\setreq{test-driven-approach}
{Must adopt a test-driven development approach with production of test plans.}
{\phigh}
{\dnone}
{\sspec}

\setreq{evidence-testing}
{Must provide evidence of testing.}
{\phigh}
{\dnone}
{\sspec}

\setreq{state-hypothesis}
{Must state hypothesis which clearly link claims to observable behaviours of your system in
  operation.}
{\phigh}
{\dnone}
{\sspec}

\setreq{valid-analysis}
{Must conduct a valid analysis of empirical data generated from an experiment (should include
  Student's t-test).}
{\phigh}
{\dnone}
{\sspec}

\setreqsec{viewing-collecting-data}{Viewing and Collecting Sleep Data}

\setreq{interface-headset}
{The system must be able to interface with the Neurosky headset.}
{\phigh}
{\ref{subreq:connect-headset}, \ref{subreq:disconnect-headset}, \ref{subreq:read-data-headset}}
{\smin{12}}

\setsubreq{connect-headset}
{The system must be able to connect to the Neurosky headset.}
{\phigh}
{\dnone}
{\smin{9}}

\setsubreq{disconnect-headset}
{The system must be able to disconnect from the Neurosky headset.}
{\phigh}
{\ref{subreq:connect-headset}}
{\smin{9}}

\setsubreq{read-data-headset}
{The system must be able to read in raw brainwave data from the Neurosky headset.}
{\phigh}
{\ref{subreq:connect-headset}}
{\smin{7}}

\setreq{store-data}
{The system must store raw brainwave data.}
{\phigh}
{\ref{subreq:facilitate-saving}, \ref{subreq:facilitate-conversion}}
{Coursework specification, meeting minutes \#7}

\setsubreq{facilitate-saving}
{The system must facilitate the saving of converted brainwave data to a binary file (.ec).}
{\phigh}
{\ref{subreq:read-data-headset}}
{\smin{12}}

\setsubreq{facilitate-conversion}
{The system must facilitate the conversion of brainwave data from binary (.ec) to CSV format.}
{\phigh}
{\ref{subreq:facilitate-saving}}
{\smin{12}}

\setreq{extract-data}
{The system should be able to extract information about sleep cycles from recorded raw data.}
{\phigh}
{\ref{subreq:extract-attention-meditation}, \ref{subreq:calculate-moving-average}}
{\smin{13}}

\setsubreq{extract-attention-meditation}
{The system should extract the attention and meditation data points from the raw brainwave data.}
{\phigh}
{\ref{req:store-data}}
{\smin{16}}

\setsubreq{calculate-moving-average}
{The system should calculate a moving average of the attention and meditation values for the whole
  data set.}
{\phigh}
{\ref{subreq:extract-attention-meditation}}
{\smin{16}}

\setsubreq{extract-sleep-percentage}
{The system must extract the percentage of time during a recording when the user was asleep vs.\
  awake.}
{\phigh}
{\ref{subreq:calculate-moving-average}}
{\smin{16}}

\setsubreq{extract-sleep-time}
{The system must calculate the time slept}
{\phigh}
{\ref{subreq:calculate-moving-average}}
{Sleep application questionnaire, meeting minutes \#16}

\setreq{present-data}
{The system should be able to present sleep cycle data to the user.}
{\phigh}
{\ref{subreq:present-data-table},\ref{subreq:present-hypnogram}}
{Coursework specification, meeting minutes \#7, sleep app questionnaire}

\setsubreq{present-data-table}
{The system should be able to present the percentage slept and the time slept in the form of a data table.}
{\phigh}
{\ref{req:extract-data}}
{\smin{17}}

\setsubreq{present-hypnogram}
{The system should be able to present processed data in the form of a line graph.}
{\phigh}
{\ref{req:extract-data}}
{Sleep app questionnaire}

\setreq{manual-entry}
{The system must permit the manual entry of the average time slept for each day over a week.}
{\pmed}
{\dnone}
{Coursework specification, sleep app questionnaire, \textcite{British-Medical-Association:2018aa}}

\setreq{apply-sorting-algorithm}
{The system should apply a ``known'' sorting algorithm which allows users to sort tracking data}
{\pmed}
{\ref{req:store-data}}
{\sspec}

\setreq{implement-cli}
{The system should implement a command-line interface allowing the user to perform all functions
  of the system.}
{\phigh}
{\ref{subreq:allow-user-record-data}, \ref{subreq:specify-time-record},
  \ref{subreq:allow-user-change-format}, \ref{subreq:allow-user-extract-calculate},
  \ref{subreq:cli-sort-display}}
{\smin{13}}

\setsubreq{allow-user-record-data}
{The command-line interface should allow the user to record data from the headset and choose where
  to store it.}
{\phigh}
{\ref{subreq:read-data-headset}, \ref{subreq:facilitate-saving}}
{\smin{13}}

\setsubreq{specify-time-record}
{The command-line interface should allow the user to specify an amount of time to record for, in
  minutes or in seconds.}
{\phigh}
{\ref{subreq:allow-user-record-data}}
{\smin{13}}

\setsubreq{allow-user-change-format}
{The command-line interface should allow the user to convert a binary (.ec) file to CSV format,
  and choose where to save the converted file.}
{\phigh}
{\ref{subreq:facilitate-conversion}}
{\smin{13}}

\setsubreq{allow-user-extract-calculate}
{The command-line interface should allow the user to extract and calculate a moving average of the
  attention and meditation data.}
{\phigh}
{\ref{subreq:calculate-moving-average}}
{\smin{16}}

\setsubreq{cli-process-sleep-data}
{The command line interface must allow the user to process sleep cycle data from a raw recorded
  data file.}
{\phigh}
{\ref{subreq:extract-sleep-percentage}}
{\smin{16}}

\setsubreq{cli-sort-display}
{The command line interface must display processed sleep cycle data in the form of a table.}
{\phigh}
{\ref{req:apply-sorting-algorithm}}
{\smin{13}}

\setreq{GUI-requiremnt}
{The system should accomodate the use of a Graphical User Interface}
{\phigh}
{\ref{subreq:allow-GUIuser-connect-disconnect}, \ref{subreq:allow-GUIuser-record-data},
  \ref{subreq:specifystart-time-record}, \ref{subreq:specifystop-time-record},
  \ref{subreq:GUIallow-user-change-format}, \ref{subreq:GUI-process-sleep-data},
  \ref{subreq:GUI-sort-display}, \ref{subreq:GUI-viewGraph}, \ref{subreq:GUI-ManageGoal}}
{Sleep application questionnaire and meeting minutes \#23}

\setsubreq{allow-GUIuser-connect-disconnect}
{The Graphical User Interface should allow the user to connect and disconnect their neurosky headset.}
{\phigh}
{\ref{subreq:connect-headset},\ref{subreq:disconnect-headset}}
{\smin{23}}

\setsubreq{allow-GUIuser-record-data}
{The Graphical User Interface should allow the user start and stop recording brainwave data
  from the headset and choose where to save it.}
{\phigh}
{\ref{subreq:read-data-headset}, \ref{subreq:facilitate-saving}}
{\smin{23}}

\setsubreq{GUIallow-user-change-format}
{The Graphical User Interface should allow the user to convert a binary (.ec) file to CSV format,
  and choose where to save the converted file.}
{\phigh}
{\ref{subreq:facilitate-conversion}}
{\smin{23}}

\setsubreq{GUIallow-playback-Data}
{The Graphical User Interface should allow the user playback their brainwave data from a selected CSV file}
{\phigh}
{\ref{subreq:allow-GUIuser-record-data}}
{\smin{23}}

\setsubreq{GUI-process-sleep-data}
{The Graphical User Interface must allow the user to process raw brainwave data stored in a user file.}
{\phigh}
{\dnone}
{\smin{23}}

\setsubreq{GUI-sort-display}
{The Graphical User Interface must display the percentage slept and the time slept in the form of a table.}
{\phigh}
{\ref{req:extract-data}}
{\smin{23}}

\setsubreq{GUI-viewGraph}
{The Graphical User Interface must allow the user to view the selected processed brainwave data in
  the form of a line graph.}
{\phigh}
{\ref{subreq:present-hypnogram}}
{Sleep app questionnaire and Meeting Minutes \#23}

\setreqsec{identifying-trends-data}{Identifying Trends in Data}

\setreq{compare-sleep-data}
{The system must allow the user to compare sleep data over a week.}
{\phigh}
{\ref{req:store-data}, \ref{req:manual-entry}}
{\textcite{British-Medical-Association:2018aa}, sleep app questionnaire}

\setreq{Automation-of-data}
{The system should permit the creation of automated data based on the user's sleep cycle}
{\pmed}
{\ref{req:store-data}}
{\smin{12}}

\setreqsec{goals-achievements}{Goals and Achievements}

\setreq{allow-manage-goals}
{Allow users to manage targets (goals) for time going to bed.}
{\pmed}
{\ref{req:store-data}, \ref{req:manual-entry}}
{Coursework specification, sleep app questionnaire}

\setreq{permit-set-goal}
{Should permit user to set a daily or weekly goal for time going to bed.}
{\pmed}
{\dnone}
{Coursework specification, meeting minutes \#7}

\setreq{update-change-goal}
{Should permit user to update or change goal.}
{\pmed}
{\dnone}
{\sspec}

\setreq{motivate-user}
{Should motivate user to achieve their goals via a point system.}
{\pmed}
{\ref{req:allow-manage-goals}, \ref{req:permit-set-goal}}
{Coursework specification, sleep app questionnaire}

\setreqsec{manage-data-periodically}{Manage Data Periodically}

\setreq{delete-data}
{Users should be given the option to delete their sleep cycle data}
{\plow}
{\ref{req:store-data}, \ref{req:extract-data}}
{Meeting minutes \#13, sleep app questionnaire}
